Transfer report

### 2019-02-15 Report/final-results.Rmd
Updates final report

## Participants
```{r}
# need revising 
# is_ok == data well measured
# finished == did finsih, regardless of potentially missing real world data
finished <- overview %>% group_by(condition) %>% count(finished)
finished <- dcast(finished, condition~finished)
finished$percent <- round(finished$yes/(finished$yes+finished$no), 2)
is_ok <- overview %>% filter(finished=="yes") %>% group_by(condition) %>% count(is_ok)
is_ok <- dcast(is_ok, condition~is_ok)
is_ok$percent <- round(is_ok$yes/(is_ok$yes+is_ok$no), 2)
```
A total of `r sum(overview$is_ok == "yes", na.rm=T) + sum(finished$no)` undergraduate students at UC Davis (M = `r round(mean(df_participants[df_participants$finished == "yes",]$age, na.rm=T),1)`, SD = `r round(sd(df_participants[df_participants$finished == "yes",]$age, na.rm=T), 1)`) particiapted in the study in exchange for a study credit. `r sum(finished$no)` participants didn't finish due to motion sickness and `r sum(is_ok$no)` were removed due to a technical failure of the real world tracking systen. Only `r finished[finished$condition == "vr-real","percent"] * 100` percent the students being able to finish Treadmill VR learning condition.

@@

3x2 repeated measures ANOVA revealed a main effect of block on distance performance, suggesting that participants improved their paths in all three conditions, `r apa_print(ez_fit_distance$aov)$statistic$exp_block_id`. The interaction effect with modality was not significant , `r apa_print(ez_fit_distance$aov)$statistic$learning_condition_exp_block_id`, suggesting that learning rate did not differ as a function of modality. In contrast, for visitation errors, we again found a main effect of block (`r apa_print(ez_fit_errors$aov)$statistic$exp_block_id`) but, importantly, a block X modality interaction effect, `r apa_print(ez_fit_errors$aov)$statistic$learning_condition_exp_block_id`. This finding suggested that visitation errors improved differently as a function of modality.

@@

finished <- overview %>% group_by(condition) %>% count(finished)
finished <- dcast(finished, condition~finished)
finished$percent <- round(finished$yes/(finished$yes+finished$no), 2)
is_ok <- overview %>% filter(finished=="yes") %>% group_by(condition) %>% count(is_ok)
is_ok <- dcast(is_ok, condition~is_ok)
is_ok$percent <- round(is_ok$yes/(is_ok$yes+is_ok$no), 2)
```
A total of `r sum(overview$is_ok == "yes", na.rm=T) + sum(finished$no)` undergraduate students at UC Davis particiapted in the second experiment. `r sum(finished$no)` participants didn't finish due to motion sickness and `r sum(is_ok$no, na.rm=T)` were removed due to a technical failure of the real world tracking system. Analyses were then conducted on a final set of `r sum(overview$is_ok == "yes", na.rm=T) ` (14 female) with mean age of `r round(mean(all_participant[all_participant$is_ok == "yes",]$age, na.rm=T),1)` (SD = `r round(sd(all_participant[all_participant$is_ok == "yes",]$age, na.rm=T), 1)`).

>>>>

## Participants
```{r}
# need revising 
# is_ok == data well measured
# finished == did finsih, regardless of potentially missing real world data
finished <- overview %>% group_by(condition) %>% count(finished)
finished <- dcast(finished, condition~finished)
finished$percent <- round(finished$yes/(finished$yes+finished$no), 2)
is_ok <- overview %>% filter(finished=="yes") %>% group_by(condition) %>% count(is_ok)
is_ok <- dcast(is_ok, condition~is_ok)
is_ok$percent <- round(is_ok$yes/(is_ok$yes+is_ok$no), 2)
kable(finished)
```

A total of `r nrow(overview)` undergraduate students at UC Davis (`r m_sd_report(df_participants[df_participants$finished == "yes",]$age)`) particiapted in the study in exchange for a study credit. `r sum(finished$no)` participants didn't finish due to motion sickness and `r sum(is_ok$no)` were removed due to a technical failure of the real world tracking systen. Only `r finished[finished$condition == "vr-real","percent"] * 100` percent the students being able to finish Treadmill VR learning condition.

@@

3x2 repeated measures ANOVA revealed a main effect of block on distance performance `r apa_print(ez_fit_distance$aov)$statistic$exp_block_id`, suggesting that participants improved their paths in all three conditions. Although the effect of the learning modality was significant (`r apa_print(ez_fit_distance$aov)$statistic$learning_condition`), the interaction between block and modality was not significant, `r apa_print(ez_fit_distance$aov)$statistic$learning_condition_exp_block_id`, suggesting that learning rate did not differ as a function of modality. In contrast, for visitation errors,  we again found a main effect of block (`r apa_print(ez_fit_errors$aov)$statistic$exp_block_id`) adn modality (`r apa_print(ez_fit_errors$aov)$statistic$learning_condition`), but, importantly, a block X modality interaction effect, `r apa_print(ez_fit_errors$aov)$statistic$learning_condition_exp_block_id`. This finding suggested that visitation errors improved differently as a function of modality.

@@

finished <- overview %>% group_by(condition) %>% count(finished)
finished <- dcast(finished, condition~finished)
finished$percent <- round(finished$yes/(finished$yes+finished$no), 2)
is_ok <- overview %>% filter(finished=="yes") %>% group_by(condition) %>% count(is_ok)
is_ok <- dcast(is_ok, condition~is_ok)
is_ok$percent <- round(is_ok$yes/(is_ok$yes+is_ok$no), 2)
```
A total of `r nrow(overview)` undergraduate students at UC Davis particiapted in the second experiment. `r sum(finished$no)` participants didn't finish due to motion sickness. Analyses were then conducted on a final set of `r sum(overview$is_ok == "yes", na.rm=T)` (14 female) participants(`r m_sd_report(all_participant[all_participant$is_ok == "yes",]$age)`).
